FoRTE baseline

### 2019-10-04 analysis/paper/paper.Rmd
Add new text and figs to results

@@

@@

>>>>

## Impacts of structure

```{r , fig.cap = structure_default_cap}
structure_default_cap <- paste(
  "Annual NPP and LAI from ED2 runs",
  "with default parameters",
  "across different configurations."
)
readd(structure_compare_default_knit)
```

Different model structures very closely for the first half of the simulation, at which point they started to diverge.
Post 1950, the combination of two-stream radiative transfer, finite canopy radius, and plastic traits had the highest sustained productivity, followed by the same configuration except with static traits, with the remaining configurations having very similar results.

```{r , fig.cap = structure_default_light_cap}
structure_default_light_cap <- paste(
  "Radiation profiles of cohorts from ED2 runs with",
  "default parameters, across different configurations."
  "Each point represents a single cohort of the given PFT,"
  "position on the y-axis represents the height of that cohort,"
  "and position on the x-axis represents the relative light level",
  "received by that cohort."
)
readd(structure_default_light_knit)
```

Differences in productivity across structures are perhaps best understood by looking at differences in resulting radiation profiles at different snapshots in time over the course of the simulation.
Enabling the finite canopy radius increased the availability of light for understory cohorts throughout the simulation, with the most notable effects up to 1950.
Under a closed canopy, switching from a two-stream to a multiple-scatter canopy radiative transfer model also enhanced the understory light environment under a closed canopy, but to a lesser extent, and the brightest understory occurred under the combination of the two-stream radiative transfer and finite canopy radius.
However, none of the configurations were able to sustain any PFTs other than early hardwoods by 1980, and only the unique combination of finite canopy radius and two-stream radiative transfer were able to sustain more than a single dominant cohort (2 early hardwood cohorts with static traits, and 3 with plastic traits).

## Default vs. median parameters

Parameter estimates from the trait meta-analysis were often substantially different from the ED2 defaults.
In many cases, median parameter estimates were different entirely because of the choice of prior distributions (though, in almost all cases, the distributions provided reasonably high likelihood to ED2 default parameter values).
However, in several important cases, parameter well-constrained by data produced values substantially different from the ED2 defaults.
For example, ED2 default values for SLA were too low for all PFTs except Early Hardwoods, and default values for Vcmax values were too low for all PFTs.

```{r , fig.cap = default_median_cap}
default_median_cap <- paste(
  "Comparing results of ED2 with default parameters and",
  "posterior median parameters from trait meta-analysis",
  "across different strucures."
)
readd(default_median_fluxes_knit)
```

```{r}
default_median_cap <- paste(
  "Comparing results of ED2 PFT-level LAI",
  "with default parameters",
  "posterior median parameters from trait meta-analysis",
  "across different strucures."
)
readd(default_median_lai_knit)
```

The above differences in median parameter led to ED2 runs that differed from the default runs in several important ways.
First of all, throughout all simulations and across all model structures, autotrophic respiration was several times higher with median parameter estimates compared to default values.
This is driven primarily by higher median values for growth and leaf respiration across all PFTs (notably, the ED2 default is a growth respiration of _zero_ for all temperate hardwood PFTs).
In some cases, this is compensated by an increase in gross primary productivity (driven by higher Vcmax values across all PFTs), leading to similar net primary productivity values to the default parameter runs.
Second, the variation across model structures is much higher, with every change in model structure exerting a noticeable effect on flux dynamics.
The most dramatic example is that, with median parameter values, all of the simulations with the finite canopy radius produced much lower productivity and heterotrophic respiration than simulations with a closed canopy.
Third, even where net primary productivity is similar between default and median runs, the underlying forest composition is very different.
Namely, under the default parameterization, ED2 produces forests dominated by Early Hardwoods, with an understory of small mid- and even smaller late-hardwood trees that eventually die out.
However, with the median parameterization, ED2 starts out with forests dominated by _mid_-hardwood species that are quickly (pre-1910 to 1930, depending on configuration) replaced with pine, which remains the dominant canopy species throughout the rest of the simulation.
Exploratory analyses (results not shown / supplement) show that the main parameters responsible for this compositional trajectory are SLA (especially the higher SLA of pine and mid-hardwood), Vcmax, and growth respiration.
While the uncertainty in growth respiration is large, we emphasize that SLA and Vcmax are well constrained by data for all PFTs considered in this analysis.

@@

<!-- - Structure x parameter uncertainty -->
<!--   - Figure: Time series of NPP, LAI, and relative PFT dominance -->
<!--   - Parameter uncertainty is much larger than structural uncertainty -->
<!--   - Figure: Pairs of NPP, LAI, and PFT fraction, for each structure (first draw all, then pick relevant subsets) -->
<!--   - Q: How many runs end up with the right composition (EH-dominated) at peak (~1925), ~1950, and 1999? -->

@@

<!-- - Details of parameter uncertainty -->
<!--   - Figure: Parameter sensitivity and uncertainty analysis -->
<!--   - Some parameters are always important. Other parameters matter more for different structures. -->
